---
title: "P8105 HW5"
author: "Wenbo Fei"
date: "11/18/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(patchwork)
```

#Problem 1
Read in the data.
```{r P1, message=F}
homicide_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

```{r 1a}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Prop test
```{r 1b}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate
```{r 1c}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

plot the results
```{r 1d}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

# Problem 2
Read and Clean the data
```{r read_n_clean, message=F}
files = list.files("data/data_2", pattern = "*.csv") # get the file name
# View(files)

data = files %>%                             
  map(~ read_csv(file.path("data/data_2", .)))  %>%  
  reduce(rbind)        # read data                       
# View(data)

# getting the arm and id 
participant = separate(data.frame(files), col=files, sep = "([._])", into =c("arm", "id")) 

participants_df = tibble(participant, data ) %>% 
  pivot_longer(                                  
    cols = week_1:week_8,
    names_prefix = "week_",
    names_to = "week",
    values_to = "value"
  )
# View(participants_df) 
```

Spagetti Plot: each line represents a participant
  
```{r 2a}
participants_df %>%
  mutate(
    unique = str_c(arm , id, sep="_") 
  ) %>%
  ggplot( aes(x = week, y = value, group = unique)) + 
  geom_line(aes(color=arm)) + 
  labs(
    title = "Spaghetti Plot"
  )
```

Control groups always stays in a relatively low value with no obvious increasing or decreasing trend, while experiment group starts with similar values to control group but has obvious overall increasing trend.

# Problem 3



